{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to SOMETHING}

### 2022-01-07 main.tex
Some theory

	Both of these can be used to express or in the case of the b-spline basis approximate elements of $\mathbb{L}^2[0,1]$ as a weighted sum of basis functions. Let therefore $\{b_i(t) \: \vert \: i \in \mathcal{I}\}$ be the basis used to express / approximate a realization $F(\omega') = f(t)$ of $F(\omega)$.

	\begin{equation}
		F(\omega') = f(t) = \sum_{j \in \mathcal{I}} \psi_j(\omega') b_j(t)
	\end{equation}

@@

	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}
	Given a realization of a random function realizing in $\mathbb{L}^2$, it is possible to represent this realization in terms of its generating stochastic process. To motivate it, recall the representation of a random vector derived from the spectral decomposition of its covariance matrix.

	\begin{equation}
		\text{{\color{red} Introduce spectral representation of random vector here.}}
	\end{equation}

	To obtain the analogous concept for a random function, it is necessary to define the covariance function of a random function realizing in $\mathbb{L}^2$. Therefore, let $F: \Omega \mapsto \mathbb{L}^2[0,1]$ be such a random function.
	Then the mean and covariance functions of $F$ are defined as follows.

@@

	The $\xi_j(\omega)$ are then given as $\xi_j(\omega) = \langle F(\omega) - \mu, \nu_j\rangle$ and thereby random variables realizing in $\mathbb{R}$.

>>>>

	Both of these can be used to express or in the case of the b-spline basis approximate elements of $\mathbb{L}^2[0,1]$ as a weighted sum of basis functions. Let therefore $\{b_i(t) \: \vert \: i \in \mathcal{I}\}$ be the basis used to express / approximate a realization $F(\omega_0) = f(t)$ of $F(\omega)$.

	\begin{equation}
		F(\omega_0) = f(t) = \sum_{j \in \mathcal{I}} \psi_j(\omega_0) b_j(t)
	\end{equation}

@@

	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}
	Given a realization of a random function realizing in $\mathbb{L}^2[0,1]$, it is possible to represent this realization in terms of its generating stochastic process. To motivate it, recall the representation of a random vector derived from the spectral decomposition of its covariance matrix. Let therefore $X(\omega)$ be a random vector realizing in $\mathbb{R}^{p}$ with $\mathbb{E}(X(\omega)) = \mu_x$ and $Cov(X(\omega)) = \Sigma_X$. Then $\Sigma_X$ can be expressed in terms of its Eigenvalues and orthonormal Eigenvectors as $\Sigma_X = \Gamma \Lambda \Gamma'$ using its Eigendecomposition.\\

	This decomposition can be used to express the random vector $X(\omega)$ in the following way.

	\begin{equation}
		X(\omega) = \mu_x + \Gamma \Lambda^{\frac{1}{2}} D(\omega) = \mu_x + \sum_{i = 1}^{p} \sqrt{\lambda_i} D_i(\omega) \gamma_i
	\end{equation}

	where $D(\omega)$ is a random vector with $\mathbb{E}(D(\omega)) = 0_p$ and $Cov(D(\omega)) = \mathbb{I}_p$.\\

	To obtain the analogous concept for a random function, it is necessary to define the covariance function of a random function realizing in $\mathbb{L}^2[0,1]$. Therefore, let $F: \Omega \mapsto \mathbb{L}^2[0,1]$ be such a random function.
	Then the mean and covariance functions of $F$ are defined as follows.

@@

	The $\xi_j(\omega)$ are then given as $\xi_j(\omega) = \langle F(\omega) - \mu, \nu_j\rangle$ and thereby random variables realizing in $\mathbb{R}$ and have the following properties akin to $\Lambda^{\frac{1}{2}} D(\omega)$ for the case of a random vector.

		\begin{multicols}{2}
		\begin{enumerate}
			\item $\mathbb{E}\left[\xi_j(\omega)\right] = 0$
			\item $Var\left(\xi_j(\omega)\right) = \lambda_i$
			\item $Cov\left(\xi_j(\omega), \xi_k(\omega)\right) = 0$ if $j \neq k$
		\end{enumerate}
	\end{multicols}
